spatial_figures

### 2024-12-16 spatial_figs.Rmd
minor updates

terrain2
``##

@@

####
rh <- ggplot() +
  geom_sf(data = hrus_map_rh, aes(fill = diff), color = "black", lwd = 0.2) +
  scale_fill_viridis_c(option = "viridis", name = "RH (%)") +
  theme_bw(base_size=15.5) +
  theme_void() + top_theme

@@

lots <- ggarrange(
  precip, sr, rh, tmean, tmax, tmin,
  heights=)

@@

ggsave("./figures/diff_update.png", plot = lots, dpi = 600)

>>>>

terrain2
##

@@

####
rh <- ggplot() +
  geom_sf(data = hrus_map_rh, aes(fill = diff), color = "black", lwd = 0.2) +
  scale_fill_viridis_c(option = "viridis", name = "RH (%)") +
  theme_bw(base_size=15.5) +
  theme_void() + bottom_theme

@@

lots <- ggarrange(
  precip, sr, rh, tmean,
  heights = 1)

@@

ggsave("./figures/diff_update2.png", plot = lots, dpi = 600)
